# Raw data {.unnumbered}

```{r set}
#| message: false
#| warning: false
library(tidyverse)
```

## Get campaign

> -   Column names need harmonization.
> -   We need data check functions.
> -   An automatic reports could be produced for errors (discussed at which level). I think the best would be at the sensor-project level with maybe a snakemake and singularity worklow or a simple R workflow to automate it with outputs in a separate place and thus sensor project databases and a single common databases (maybe sqlight for big ones).
> -   Reading functions will depend on the sensors and will need to be made generic on the way they open and handle data.
> -   We need to had soil data or parameters for soil moisture.
> -   Date filtering should be used the earliest to save memory.

```{r functions}
read_data <- function(
    path,
    utc,
    start_date,
    stop_date
) {
  decimal <- read_delim(path, col_select = 5, col_names = F, 
           delim = ";", col_types = list(X5 = col_character()), n_max = 1)$X5 %>% 
    gsub("[^[:punct:]]", "", .)
  if(str_length(decimal) == 0)
    decimal <- read_delim(path, col_select = 5, col_names = F, 
           delim = ";", col_types = list(X5 = col_character()), n_max = 2)$X5[2] %>% 
      gsub("[^[:punct:]]", "", .)
  read_delim(path, col_names = FALSE, locale = locale(decimal_mark = decimal),
          col_select = c(2, 4:7)) %>% 
    mutate(X2 = gsub(".", "-", X2, fixed = TRUE)) %>% 
    mutate(X2 = as.POSIXct(X2)) %>% 
    mutate(X2 = as_datetime(X2)) %>% 
    rename(date = X2, t_soil = X4, 
           t_surface = X5, t_air = X6, moisture = X7) %>% 
    mutate(date = date + utc*60*60) %>% 
    filter(as_date(date) >= start_date) %>% 
    filter(as_date(date) < stop_date)
}
get_tomst_campaign <- function(
    path,
    metadata,
    metadatac,
    utc,
    start_date,
    stop_date
    ) {
  files <- list.files(path, pattern = "data", full.names = TRUE)
  names(files) <- list.files(path, pattern = "data", full.names = FALSE)
  data <- files %>% 
    lapply(read_data, utc, start_date, stop_date) %>% 
    bind_rows(.id = "file") %>% 
    separate(file, c("data", "sensornum"), convert = T) %>% 
    select(-data)
  metadata <- readxl::read_xlsx(metadata) %>% 
    select(TomstID, TomstSensorNum) %>% 
    rename(id = TomstID, sensornum = TomstSensorNum)
  metadatac <- readxl::read_xlsx(metadatac) %>% 
    rename_all(tolower)
  data <- metadata %>% 
    left_join(metadatac) %>% 
    full_join(data)
  return(data)
}
```

```{r test_campaign}
#| eval: false
data <- get_tomst_campaign(
  path = "data/Paracou/TOMST_ALT/20240920/",
  metadata = "data/Paracou/TOMST_ALT/TOMST_ALT.xlsx",
  metadatac = "data/Paracou/TOMST_ALT/20240920.xlsx",
  utc = -3,
  start_date = as_date("20230401"),
  stop_date = as_date("20240920")
)
write_tsv(data, "tests/test_campaign.tsv")
```

```{r test_campaign_res}
#| message: false
#| warning: false
read_tsv("tests/test_campaign.tsv", n_max = 20) %>% 
  head() %>% 
  knitr::kable()
```

```{r test_campaign_res2}
#| message: false
#| warning: false
read_tsv("tests/test_campaign.tsv") %>% 
  filter(id == 1) %>% 
  ggplot(aes(date, t_air)) +
  geom_line() +
  theme_bw()
```

## Get sensor-project

> -   To automate, by end for the moment with the three folders.
> -   This is heavy in memory so it should be automated with a wrokflow based on intermediary files.

```{r get_sensor-project}
#| eval: false
data1 <- get_tomst_campaign(
  path = "data/Paracou/TOMST_ALT/20240920/",
  metadata = "data/Paracou/TOMST_ALT/TOMST_ALT.xlsx",
  metadatac = "data/Paracou/TOMST_ALT/20240920.xlsx",
  utc = -3,
  start_date = as_date("20230401"),
  stop_date = as_date("20240920")
)
data2 <- get_tomst_campaign(
  path = "data/Paracou/TOMST_ALT/20250418/",
  metadata = "data/Paracou/TOMST_ALT/TOMST_ALT.xlsx",
  metadatac = "data/Paracou/TOMST_ALT/20250418.xlsx",
  utc = -3,
  start_date = as_date("20240920"),
  stop_date = as_date("20250418")
)
data3 <- get_tomst_campaign(
  path = "data/Paracou/TOMST_ALT/20250930/",
  metadata = "data/Paracou/TOMST_ALT/TOMST_ALT.xlsx",
  metadatac = "data/Paracou/TOMST_ALT/20250930.xlsx",
  utc = -3,
  start_date = as_date("20250418"),
  stop_date = as_date("20250930")
)
data <- bind_rows(data1 %>% mutate(field = as.character(field)), data2, data3)
write_tsv(data, "tests/test_sensor-project.tsv")
```

```{r get_sensor-project_res1}
#| message: false
#| warning: false
read_tsv("tests/test_sensor-project.tsv") %>% 
  filter(id == 1) %>% 
  ggplot(aes(date, t_air)) +
  geom_line() +
  theme_bw() +
  geom_vline(xintercept = c(
    as_datetime("2024-09-20 00:00:00"),
    as_datetime("2025-04-18 00:00:00")
  ), col = 'lightgrey') +
  ggtitle("Sensor 1")
```

```{r get_sensor-project_res}
#| message: false
#| warning: false
read_tsv("tests/test_sensor-project.tsv") %>% 
  filter(id == 32) %>% 
  ggplot(aes(date, t_air)) +
  geom_line() +
  theme_bw() +
  geom_vline(xintercept = c(
    as_datetime("2024-09-20 00:00:00"),
    as_datetime("2025-04-18 00:00:00")
  ), col = 'lightgrey') +
  ggtitle("Sensor 32")
```

## Assemble

> To test when using multples sensors and/or project and even sites.
