# Raw data {.unnumbered}

```{r set}
#| message: false
#| warning: false
library(tidyverse)
```

## Campaign - Paracou TOMST ALT 2024/09\*20

> - Column names need harmonization.
> - We need data check functions.
> - An automatic reports could be produced for errors (discussed at which level). I think the best would be at the sensor-project level with maybe a snakemake and singularity worklow or a simple R workflow to automate it with outputs in a separate place and thus sensor project databases and a single common databases (maybe sqlight for big ones).
> - Reading functions will depend on the sensors and will need to be made generic on the way they open and handle data.
> - We need to had soil data or parameters for soil moisture.
> - Date filtering should be used the earliest to save memory.

```{r functions}
source("scripts/read_tomst_data.R")
source("scripts/read_tomst_campaign.R")
source("scripts/read_sensor_project.R")
```

```{r test_campaign}
#| eval: false
data <- read_tomst_campaign(
  path = "data/Paracou_TOMST_ALT/20240920/",
  metadata = "data/Paracou_TOMST_ALT/metadata.xlsx",
  metadata_campaign = "data/Paracou_TOMST_ALT/20240920.xlsx",
  utc = -3,
  start_date = as_date("20230401"),
  stop_date = as_date("20240920")
)
write_tsv(data, "tests/Paracou_TOMST_ALT_20240920.tsv")
```

```{r test_campaign_res}
#| message: false
#| warning: false
read_tsv("tests/Paracou_TOMST_ALT_20240920.tsv", n_max = 20) %>% 
  head() %>% 
  knitr::kable()
```

```{r test_campaign_res2}
#| message: false
#| warning: false
read_tsv("tests/Paracou_TOMST_ALT_20240920.tsv") %>% 
  filter(id == 1) %>% 
  ggplot(aes(date, t_air)) +
  geom_line() +
  theme_bw()
```

## Dataset - Paracou TOMST ALT 

> - To automate, by hand for the moment with the three folders.
> - This is heavy in memory so it should be automated with a workflow based on intermediary files.

```{r get_sensor-project}
#| eval: false
data <- read_sensor_project(
  path = "data/Paracou_TOMST_ALT/",
  sensor = "TOMST"
)
write_tsv(data, "tests/Paracou_TOMST_ALT.tsv")
```

```{r get_sensor-project_res_all}
#| message: false
#| warning: false
#| fig-width: 10
#| fig-height: 10
read_tsv("tests/Paracou_TOMST_ALT.tsv") %>% 
  ggplot(aes(date, t_air)) +
  geom_line() +
  theme_bw() +
  geom_vline(xintercept = c(
    as_datetime("2024-09-20 00:00:00"),
    as_datetime("2025-04-18 00:00:00")
  ), col = 'lightgrey') +
  facet_wrap(~ id) + 
  ylim(15, 40)
```

## Assemble

> To test when using multiples sensors and/or project and even sites.
