# Paracou TOMST ALT {.unnumbered}

```{r set}
#| message: false
#| warning: false
library(tidyverse)
```

## Preparation

This is the chunk to manually prepare the dataset, this should be automated in the future.

```{r prep}
#| eval: false
source("scripts/read_tomst_data.R")
source("scripts/read_tomst_campaign.R")
source("scripts/read_sensor_project.R")
data <- read_sensor_project(
  path = "data/Paracou_ALT_TOMST/",
  sensor = "TOMST"
)
write_tsv(data, "datasets/Paracou_ALT_TOMST.tsv")
```

## Campaigns

Currently available campaigns are:

```{r campaigns}
#| message: false
#| warning: false
readxl::read_xlsx("data/Paracou_ALT_TOMST/campaigns.xlsx") |> knitr::kable()
```

## Dataset

```{r tab}
#| message: false
#| warning: false
read_tsv("datasets/Paracou_ALT_TOMST.tsv", n_max = 20) %>% 
  head() %>% 
  knitr::kable()
```

```{r fig}
#| message: false
#| warning: false
#| fig-width: 10
#| fig-height: 10
read_tsv("datasets/Paracou_ALT_TOMST.tsv") %>% 
  ggplot(aes(date, t_air)) +
  geom_line() +
  theme_bw() +
  geom_vline(xintercept = c(
    as_datetime("2024-09-20 00:00:00"),
    as_datetime("2025-04-18 00:00:00")
  ), col = 'lightgrey') +
  facet_wrap(~ id) + 
  ylim(15, 40)
```

## Other files

> To be described.

## To do

> - To automate, by hand for the moment with the three folders.
> - This is heavy in memory so it should be automated with a workflow based on intermediary files.
